---
title: "Week6_Lab"
author: "Elena Ortiz"
date: "11/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(ggpubr)
```

## Week 6 Coding: Intro to Linear Regression 

### Part 1: Rank-based test example (Mann Whitney U)

Comparing ranks (medians comparison) between more than 2 samples using wilcox.test()

```{r}
set.seed(1414) #create random samples with integers from 1 to x
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Initial exploration of data

```{r}
hist(gp_1)

hist(gp_2)
```
Why comparing ranks here: 
1. Not clearly normally distributed
2. Somewhat small sample size (n =15)
3. I've decided medians more valuable metric

Here we'll use a Mann-Whitney U to answer: "is there a significant difference in ranks (medians) between gp_1 and gp_2?"

```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
```

Here we get a p-value of 0.28. This means that if the null hypothesis is true and these samples we drawn from populations with the same median, there is a 28% chance that we would find a difference in medians at least as different as we found if the samples were drawn randomly. Not enough to reject the null hypothesis if using a p-value of .05.  

### Sample linear regression 

Explore the relationship between flipper length and body mass for penguins, including all three penguin species in the palmerpenguins dataset. 

#### First, view data 

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point()
```
Here, looks like an overall linear relationship between flipper length and body mass makes sense. 

#### Model the data using lm()

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins) #linear model, stored as penguin_lm

#Return the complete overview
summary(penguin_lm)
```

Multiple R^2 value is 0.759, meaning that 75.9% of variance in body mass is explained by flipper length. 

#### Access model outputs 

Slope: 49.69 (g/mm)
y-intercept: -5780.83 (g)
full equation is mass = 49.69*(flipper length) + (-5780.83)

Use broom::tidy() to get outputs into a nice format. 

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

#intercept
penguin_int <- penguin_lm_tidy$estimate[1]

#Flipper length coefficient
penguin_coef <- penguin_lm_tidy$estimate[2]
```

Other info can come from broom::glance()

```{r}
#Metrics at a glance
penguin_lm_out <- broom::glance(penguin_lm)
```

#### Explore model assumptions

```{r}
plot(penguin_lm)
```

#### Visualize the model

